Precision Fundamental Stellar Properties with Interpretable Machine Learning

### 2023-11-30 paper/paper2/ms.tex
Line density figure addition
First draft of the flowcharts, split into steps 1-3 and 4-6
Generate plots

\begin{document}
\title{Estimating Fundamental Stellar Properties using PHOENIX Grid Interpolators}

@@

@@

\begin{mdframed}
    \textbf{Figure: Line density across the grid heatmap}
\end{mdframed}

@@

\begin{mdframed}
    \textbf{Figure: Heatmap $\Teff$ vs $\logg$ for a single line $2\times2$ panels for $\sigma$, $\gamma$, $A$, $\lambda$ }
\end{mdframed}

@@

\section{Mapping Line Parameters to Fundamental Properties}
\begin{mdframed}
    \textbf{Statement: A Bidirectonal Relation exists}
    - Goal: identify a functional form
    \textcolor{lightgray}{\blindtext}
\end{mdframed}

\begin{mdframed}
    \textbf{Figure: Flowchart-with-equations}
\end{mdframed}

>>>>

\begin{document}
\title{Precision Fundamental Stellar Properties with Interpretable Machine Learning}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{images/flowchart_frame1_v0p3.png}
    \caption{Flowchart of the cloning steps for emulating precomputed spectra.}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{images/line_density.png}
    \caption{Heatmap of the number of spectral lines detected at each grid point.
    The grid has been sliced at solar metallicity to make the heatmap 2D.}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{images/heatmap0.png}
    \caption{Heatmap of the most commonly detected spectral line at 8185.51 Angstroms. Amplitude,
    Gaussian shape, and Lorentzian shape are on a logarithmic scale. Jitter is a measure of how 
    much \texttt{blase} shifted the line center during cloning.}
\end{figure*}

@@

\section{Mapping Line Parameters to Fundamental Properties}
\begin{mdframed}
    \textbf{Statement: A Bidirectonal Relation exists}

    Now that we have our list of line properties for each grid point, we need to find the link 
    between these line properties and the fundamental stellar parameters. We know that there is
    some relation between the two, but we do not even know its functional form. While we have a
    ridiculously large array of methods to choose from, we can start with a simple linear
    regression with a polynomial basis. We can quickly test the efficacy of this method by 
    running it on the line we visualized earlier.
\end{mdframed}

\begin{figure*}
    \includegraphics[width=\textwidth]{images/heatmap_poly.png}
\end{figure*}

\begin{mdframed}
    \textbf{Big equation section}
\end{mdframed}

\begin{figure*}
    \includegraphics[width=\textwidth]{images/flowchart_frame2_v0p3.png}
    \caption{Flowchart of the manifold steps for reconstructing a precomputed spectrum.}
\end{figure*}
